%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------


\cvsection{Publication}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{footnotesize}

\begin{itemize}[leftmargin=2ex, nosep, noitemsep]
	% ----------------------------------------
	
	\item {\textbf{Zhou, Z.}, Unjhawala, H, Kamaraj, A, Kissel, A, Lee, J, Serban, R, Negrut, D,  "A Chrono-Based Framework for Large-Scale Traffic Simulation with Human-In-The-Loop." Proceedings of the \textit {Multibody 2023 11th ECCOMAS Thematic Conference on Multibody Dynamics}, Lisboa, Portugal. July 24-28, 2023. Preprint \url{https://doi.org/10.13140/RG.2.2.23133.59361}}
	
	% ----------------------------------------
	
	\item {Serban, R, Taves, J, \textbf{Zhou, Z.} "Real-Time Simulation of Ground Vehicles on Deformable Terrain." Proceedings of the \textit {ASME 2022 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference. Volume 9: 18th International Conference on Multibody Systems, Nonlinear Dynamics, and Control (MSNDC).} St. Louis, Missouri, USA. August 14–17, 2022. V009T09A012. ASME. \url{https://doi.org/10.1115/DETC2022-89470}}
	
	% ----------------------------------------
	
	\item {Hu, W., \textbf{Zhou, Z.}, Chandler, S., Apostolopoulos, D., Kamrin, K., Serban, R., Negrut, D. Traction control design for off-road mobility using an SPH-DAE cosimulation framework. \textit {Multibody Syst Dyn} 55, 165–188 (2022). \url{https://doi.org/10.1007/s11044-022-09815-2}}
	
	% ----------------------------------------
	
	\item {Hu, W., \textbf{Zhou, Z.}, Serban, R., Negrut, D., Using an SPH-based continuum representation of granular terrain to simulate VIPER rover mobility, 2021/10, \textit{Preprint}, \url{https://www.researchgate.net/publication/358872957_Off-Road_Rover_Mobility_Simulation_Using_a_Continuum_Representation_of_Deformable_Terrains}}
	
	% ----------------------------------------
	
	\item {Hu, W, \textbf{Zhou, Z}, Serban, R, Negrut, D. "Using an SPH-Based Continuum Representation of Granular Terrain to Simulate the Rover Mobility." Proceedings of the \textit{ASME 2021 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference. Volume 9: 17th International Conference on Multibody Systems, Nonlinear Dynamics, and Control (MSNDC)}. Virtual, Online. August 17–19, 2021. V009T09A028. ASME. \url{https://doi.org/10.1115/DETC2021-71289}}

\end{itemize}
	
\end{footnotesize}


